Token-level author diarization using clustering of stylistic contexts

### 2017-06-01 paper/paper.tex
Started intro to chapter 5.

We implemented two variants of our final model, first with only a basic feature extractor $f_\mathrm{b}$ whether in second feature transformation $f_\mathrm{t}$ was used. For the first variant, where only a basic feature extractor $f_\mathrm{b}$ was used, we extracted features for each document separately. In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents were concatenated to a single one from which basic and transformed feature vectors were obtained. In both approaches features were extracted from a sliding window which included a context of each token.

@@

The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens. The number of clusters was equal to the number of authors in tasks $a$ and $b$, but in task $c$ it was unknown. We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org/stable/}} Python toolkit in all tasks. For tasks $a$ and $b$ we propose hierarchical agglomerative clustering, and for task $c$ DBSCAN algorithm which estimates the number clusters automatically. The reason of choosing that algorithms is described below.

@@

>>>>

We implemented two variants of our final model. First is with only a basic feature extractor $f_\mathrm{b}$, whether in second the feature transformation $f_\mathrm{t}$ was used. For the first variant, where only a basic feature extractor $f_\mathrm{b}$ was used, we extracted features for each document separately. In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents were concatenated to a single one from which basic and transformed feature vectors were obtained. In both approaches basic features were extracted from a sliding window which moved from token to token and included a context of each token. In the rest of the paper we refer to the first variant as model A, and to the second as model B.

@@

The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens. The number of clusters was equal to the number of authors in tasks $a$ and $b$, but in task $c$ it was unknown. We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org/stable/}} Python toolkit by \citet{scikit-learn} in all tasks. In the first variant of our approach for tasks $a$ and $b$ we propose hierarchical agglomerative clustering, and for task $c$ DBSCAN algorithm which estimates the number of clusters automatically. In the second variant we used k-means for clustering in tasks $a$ and $b$, and our modification of k-means, which we called AutoKmeans in task $c$. The reason of choosing that algorithms is described in chapter ????? 5 ????.

@@

We performed initial testing of usefulness of all features except accidentally wrong implemented type-token ratio which was added afterwards. For testing purposes we used k-means algorithm with default settings available in \texttt{scikit-learn} and all documents from task $b$ dataset. As we added feature by feature, BCubed precision was higher so we decided to extract all features in all tasks. We don't know the exact impact of wrongly implemented type- token ratio. Instead of the context's vocabulary size, we divided the size of document's vocabulary with the context size so this feature had the same value in all vectors.

Five baseline models were defined for evaluation purposes. First baseline, \textit{DummySingleAuthorDiarizer} always assigned all tokens to only one cluster, assuming that text is written by a single author. As we will later describe, this baseline model behaved very competitive. The second baseline was \textit{DummyStohasticAuthorDiarizer} which generated a random number between
